Next Trippy Structures\thanks{Supported by organization x.}

### 2019-07-12 paper.tex
Abstract Daniil

\newcommand{\acumm}{T-Matrices} % T is for Total!
\newcommand{\acummname}{\mathsf{Trip-Matrices}}
\newcommand{\ctr}{XCTR}
\newcommand{\ctrname}{\mathsf{eXtended~Compact~Trip~Representation}}
\newcommand{\ttctr}{TTCTR}
\newcommand{\ctrq}{$\alpha$}
\newcommand{\ttctrq}{$\beta$}
\newcommand{\ttctrname}{\mathsf{Topology\&Trip-aware~Compact~Trip~Representation}}

@@

\begin{document}
%
\title{New Trippy Structure \thanks{Funded in part by European Union`s Horizon 2020 research and innovation programme
under the Marie Sklodowska-Curie grant agreement No 690941 (project
BIRDS). The Spanish group is also partially funded by Xunta de Galicia/FEDERUE
[CSI: ED431G/01; GRC: ED431C 2017/58; GEMA:IN852A
2018/14 and Innovapeme: IN848D-2017-2350417]; by MINECO-AEI/FEDER-UE
[Datos 4.0: TIN2016-78011-C4-1-R; and ETOMERDFD3:
TIN2015-69951-R]; and by FPI Program [BES-C-2017-0085]. M. A. Rodr´ıguez is
partially funded by Fondecyt-Conicyt grant number 1170497 and by the Millennium
Institute for Foundational Research on Data. }}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Nieves R. Brisaboa\inst{1} \and
Antonio Fari\~na\inst{1}\and
Daniil Galaktionov\inst{1,2} \and Tirso V. Rodeiro\inst{1} \and M. Andrea Rodr\'iguez\inst{3,4}}
%
\authorrunning{N. Brisaboa et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universidade da Coru\~na, Laboratorio de Bases de Datos, A Coru\~na, Spain  \email{\{brisaboa, fari, d.galaktionov, tirso.varela.rodeiro\}@udc.es}  \and 
Enxenio S.L., A Coru\~na, Spain
\and
Computer Science Department, Universidad de Concepci\'on, Concepci\'on, Chile \and Millennium Institute for Foundational Research on Data, Santiago, Chile
\email{andrea@udec.cl }\\
 }
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

>>>>

\newcommand{\acumm}{T-Matrices} % T is for Trips!
\newcommand{\acummname}{\mathsf{Trip-Matrices}}
\newcommand{\ctr}{XCTR}
\newcommand{\ctrname}{\mathsf{eXtended~Compact~Trip~Representation}}
\newcommand{\ttctr}{TTCTR}
\newcommand{\ctrq}{$\alpha$}
\newcommand{\ttctrq}{$\beta$}
\newcommand{\ttctrname}{\mathsf{Topology\&Trip-aware~Compact~Trip~Representation}}

@@

\begin{document}
%
\title{Improved structures to solve aggregated queries for trips over public transportation networks \thanks{Funded in part by European Union`s Horizon 2020 research and innovation programme
under the Marie Sklodowska-Curie grant agreement No 690941 (project
BIRDS). The Spanish group is also partially funded by Xunta de Galicia/FEDERUE
[CSI: ED431G/01; GRC: ED431C 2017/58; GEMA:IN852A
2018/14 and Innovapeme: IN848D-2017-2350417]; by MINECO-AEI/FEDER-UE
[Datos 4.0: TIN2016-78011-C4-1-R; and ETOMERDFD3:
TIN2015-69951-R]; and by FPI Program [BES-C-2017-0085]. M. A. Rodr´ıguez is
partially funded by Fondecyt-Conicyt grant number 1170497 and by the Millennium
Institute for Foundational Research on Data. }}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Nieves R. Brisaboa\inst{1} \and
Antonio Fari\~na\inst{1}\and
Daniil Galaktionov\inst{1,2} \and Tirso V. Rodeiro\inst{1} \and M. Andrea Rodr\'iguez\inst{3,4}}
%
\authorrunning{N. Brisaboa et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universidade da Coru\~na, Laboratorio de Bases de Datos, A Coru\~na, Spain  \email{\{brisaboa, fari, d.galaktionov, tirso.varela.rodeiro\}@udc.es}  \and 
Enxenio S.L., A Coru\~na, Spain
\and
Computer Science Department, Universidad de Concepci\'on, Concepci\'on, Chile \and Millennium Institute for Foundational Research on Data, Santiago, Chile
\email{andrea@udec.cl }\\
 }
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In order to efficiently store and analyze large datasets of passenger trips over public transportation networks, one promising approach is the use of a representation based of compact data structures.

In this work we propose a solution based on two complementary representations, \acumm~and~\ttctr, with an alternative for the later called \ctr. Overall, with our representations we were able to store a dataset of ten million trips in around 100 MB, supporting a wide range of queries in the order of microseconds.
